\documentclass[output=paper]{langsci/langscibook} 

\title{Do Semantic Features Capture a Syntactic Classification of Compounds? Insights from Compositional Distributional Semantics} 

\author{%
 Sandro Pezzelle\affiliation{CIMeC - Center for Mind/Brain Sciences, University of Trento}\lastand
 Marco Marelli\affiliation{Department of Psychology, University of Milano-Bicocca}
}

%\chapterDOI{} %will be filled in at production

% \epigram{}

\abstract{Classifying compound words has been the ultimate goal of a considerable number of studies in the field of formal linguistics. Various criteria have been proposed, such as the notion of `headedness', the presence of a verb, the kind of syntactic relation between the constituent words, and so on. A popular, cross-linguistically applicable classification \citep{SB2005} distinguished three main types of compounds, namely Subordinate, Attributive, and Coordinate on the basis of the underlying \textit{syntactic} relation between the compound elements. Similar tripartitions have been also proposed in the field of cognitive psychology by work exploring conceptual combination. Focusing on the type of \textit{semantic} interpretation assigned to novel combinations, three main classes have been traditionally identified, namely Relation-linking, Property-mapping, and Hybrid or Conjunctive (see \cite{wisniewski1996}). Based on these commonalities, we conjecture that syntax-based compound types might be also explained by means of the semantic properties of the compound and its constituents. Using a compositional model of distributional semantics (cDSM), we show that both (a) the contribution of each constituent in determining the meaning of the compound and (b) the semantic similarity between the two constituent words are significant predictors of these classes. These findings suggest that the various compound types identified by syntactic criteria can be also predicted by means of semantic features. On the one hand, this evidence confirms the validity of the proposed linguistic categorization. On the other hand, we bring further evidence proving the effectiveness of cDSMs in describing linguistic phenomena.}

\begin{document}
\maketitle


\input{chapters/pezzele/introduction.tex}
\input{chapters/pezzele/experiments}
\input{chapters/pezzele/results}
\input{chapters/pezzele/discussion}





%\section*{Abbreviations}
\section*{Acknowledgements}
We are grateful to Marco Baroni and Laura Vanelli for their valuable feedback during the early stages of the project. We thank Sergio Scalise for providing the MorBoComp subset used in the experiment. We are also grateful to the participants of the First Quantitative Morphology Meeting (Belgrade, July 2015) for the helpful questions and discussion.


{\sloppy
\printbibliography[heading=subbibliography,notkeyword=this]
}


\end{document}
